Key Derivation From Noisy Sources With More Errors Than Entropy

### 2014-04-14 constantRate/ConstCompFuzzExt-eprint.tex
Grant numbers for eprint

\title{Key Derivation From Noisy Sources With More Errors Than Entropy}
\author{Ran Canetti\footnote{Email: {\tt canetti@cs.bu.edu}.} ~~~~~ Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.  Work done in part while the author was at MIT Lincoln Laboratory.} ~~~~~ Omer Paneth\footnote{Email: {\tt paneth@cs.bu.edu}. } ~~~~~ Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.} \\ Boston University }

@@

\section*{Acknowledgements}
The authors are grateful to Nir Bitanski, Nishanth Chandran, Sharon Goldberg, Gene Itkis, Bhavana Kanukurthi, Adam Smith, and Mayank Varia for helpful discussions, creative ideas, and important references.

This work is supported in part by National Science Foundation grants XXXX. The work of Benjamin Fuller is sponsored in part by the United States Air Force under Air Force Contract FA8721-05-C-0002. Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.  
\bibliographystyle{alpha}
\bibliography{crypto}

>>>>

\title{Key Derivation From Noisy Sources With More Errors Than Entropy}
\author{Ran Canetti\footnote{Email: {\tt canetti@cs.bu.edu}. Boston University and Tel Aviv University.} \and Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.  Boston University and MIT Lincoln Laboratory.} \and Omer Paneth\footnote{Email: {\tt paneth@cs.bu.edu}. Boston University.} \and Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.  Boston University.} }

@@

\section*{Acknowledgements}
The authors are grateful to Nishanth Chandran, Sharon Goldberg, Gene Itkis, Bhavana Kanukurthi, Adam Smith, and Mayank Varia for helpful discussions, creative ideas, and important references.

This work is supported in part by National Science Foundation grants 0831281, 1012910, 1012798, and 1218461. 
Omer Paneth is additionally supported by the Simons award for graduate students in theoretical computer science.
The work of Benjamin Fuller is sponsored in part by the United States Air Force under Air Force Contract FA8721-05-C-0002. Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.
\bibliographystyle{alpha}
\bibliography{crypto}
